Approximate Network Matching

### 2024-02-20 paper.qmd
update paper.qmd

The terminology to refer to the two FeatureCollections is inconsistent. For example, Zhang (@zhang_2009) refers to the two FeatureCollections as the **reference** and **target** whereas the Java Conflation Suite (JCS) (@jcs) refers to these as the **reference** and **subject**.

We will use the terms _reference_ FeatureCollection and _subject_ FeatureCollection. The objective of the matching algorithm is to match features _from_ the subject _to_ the reference. Often the reference is a more detailed and known collection of features.

In the process matching features, **candidate**s are found. A candidate is a subject feature that may correspond to a reference feature. If a candidate passes tests, it is then deemed a match. After matches have been found, attributes from the source feature are often transferred to the reference feature. This process of attribute transfer is referred to as **integration**.

@@

>>>>

The terminology to refer to the two FeatureCollections is inconsistent in the literature. For example, Zhang (@zhang_2009) refers to the two FeatureCollections as the reference and target whereas the Java Conflation Suite (JCS) (@jcs) refers to these as the reference and subject.

We intentionally lean on terminology used in relational database management systems (RDBMS), instead recognizing a shift towards spatial data science which incorporates RDBMS tools. We define the two FeatureCollections as **target** and the **source**. The objective of the matching algorithm is to match features _from_ the source _to_ the target. Often the target is a more detailed and known collection of features.

In the process matching features, **candidate**s are found. A candidate is a source feature that _may_ correspond to a target feature. If a candidate passes tests, it is then deemed a match. After matches have been found, attributes from the source feature are often transferred to the target feature. This process of attribute transfer is referred to as **integration**.

@@

- a feature in the source and target may only be matched a maximum of once. 
- the shared length between i and j may exceeed the total length of i or j. This occurs in parallel ways and larger distance tolerances
